Using Probabilistic Knockoffs of Binary Variables to Control the False Discovery Rate

### 2015-07-10 masters_paper/notes.tex
Added FDR calculations

\documentclass[11pt]{article}
\usepackage[paper=letterpaper, margin=.5in]{geometry}
\linespread{1.5}
\pdfpagewidth 8.5in
\pdfpageheight 11in

@@

\begin{document}
\title{Binary Knockoffs Notes}
\author{Aaron Maurer}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preliminaries} 
    {\em Note:} I will try to hold to the convention that $X$ is the $n\times p$ data matrix, while $\bf x$ is the random vector variable from which each row of $X$ was drawn. Accordingly, $\tilde X$ will be the knockoff matrix while $\bf \tilde x$ is a random vector variable. $x_i$ will be the random variable corresponding to the $i$th entry of $\bf x$, while $X_i$ is the vector of observations drawn from $x_i$ in the data matrix. $\hat \Sigma = \frac{1}{n}X^TX$ is the empirical covariance matrix associated with $X$, while $\Sigma=\E(\mathbf x \mathbf x^T)$ is the theoretical covariance matrix associate with $\mathbf x$. Also, for a square matrix $A$, $\diag(A)$ if the vector of values along the diagonal, while for a vector $\mathbf a$, $\diag(\mathbf a)$ is a square diagonal matrix with $\mathbf a$ along the diagonal.\\

    Some early investigation into deterministic knockoffs (as described in the original knockoff paper) reveal that they don't perform well in L1 regularized logistic regression. Even when $X_i$ is a null predictor of $y$, the $X_i$ still tend to enter the model prior to $\tilde X_i$. The issue is that even when $x\sim N_p({\bf 0}, \Sigma)$ for some $\Sigma\succeq 0$, $\tilde x$ is not normally distributed. This can be seen from producing qq plots of $X_i$ vs $\tilde X_i$ for each $i$. Of course, when $X$ is a binary vector, $\tilde X$ completely doesn't match its distribution, causing the original $X$ to beat the knockoffs into the model. This indicates that a new method of generating $\tilde X$ must be created to control FDR via knockoffs with regularized logistic regression.

>>>>

\documentclass[11pt]{article}
\usepackage[paper=letterpaper, margin=1in]{geometry}
\linespread{1.5}
\pdfpagewidth 8.5in
\pdfpageheight 11in

@@

\begin{document}
\title{Using Probabilistic Knockoffs of Binary Variables to Control the False Discovery Rate}
\author{Aaron Maurer}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
    Basic overview of what paper is about

\subsection{Knockoff Filter}
    Describe the original knockoff filter,

\subsection{Binary Knockoffs}
    Overview of my addition

\section{Issues With Deterministic Knockoffs} 
    {\em Note:} I will try to hold to the convention that $X$ is the $n\times p$ data matrix, while $\bf x$ is the random vector variable from which each row of $X$ was drawn. Accordingly, $\tilde X$ will be the knockoff matrix while $\bf \tilde x$ is a random vector variable, at least when $\tilde X$ is generated randomly. $x_i$ will be the random variable corresponding to the $i$th entry of $\bf x$, while $X_i$ is $i$th column of $X$, with observations drawn from $x_i$. $\hat \Sigma = \frac{1}{n}X^TX$ is the empirical covariance matrix associated with $X$, while $\Sigma=\E(\mathbf x \mathbf x^T)$ is the theoretical covariance matrix associate with $\mathbf x$. Also, for a square matrix $A$, $\diag(A)$ is the vector of values along the diagonal, while for a vector $\mathbf a$, $\diag(\mathbf a)$ is a square diagonal matrix with $\mathbf a$ along the diagonal.\\

    Simulations with deterministic knockoffs reveal that they don't perform well in L1 regularized logistic regression. Even when $X_i$ is a null predictor of $y$, the $X_i$ still tend to enter the model prior to $\tilde X_i$. The issue is that even when $x\sim N_p({\bf 0}, \Sigma)$ for some $\Sigma\succeq 0$, the $\tilde X_i$ do not fit a normal distribution. This can be seen below in figure 1, where normal Q-Q plots of simulated variables $X_i$ and corresponding knockoffs $\tilde X_i$ are provided.
    \begin{figure}[h!]
        \includegraphics[width=20cm]{images/normalQQ}
        \caption{Normal Q-Q of original variables and knockoffs for simulation with $4$ variables and 1,000 observations}
    \end{figure}

    This can be seen from producing qq plots of $X_i$ vs $\tilde X_i$ for each $i$. Of course, when $X$ is a binary vector, $\tilde X$ completely doesn't match its distribution, causing the original $X$ to beat the knockoffs into the model. This indicates that a new method of generating $\tilde X$ must be created to control FDR via knockoffs with regularized logistic regression.
